---
title: "Bernoulli Distribution"
author: "Sebastián Sánchez Sandí"
date: "2025-07-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let $X$ be a random variable. If X \~ Bernoulli(p), then it follows a Bernoulli distribution. The probability mass function is given by:

$$
f(x) = \begin{cases} p^x(1-p)^{1-x} &
\text{if }  x \in \{0, 1\} \\ 0 &
\text{if } x \notin \{0, 1\} \end{cases}
$$

Where $p \in [0, 1]$.

-   $E(X)=p$

-   $Var(X)=p(1-p)$

This distribution models scenarios with only two possible outcomes: successand failure. A common example is flipping a fair coin, where the probability of heads (success) is $\frac{1}{2}$ and the probability of tails (failure) is also $\frac{1}{2}$.

```{r echo=FALSE}
library(ggplot2)

n = 1
p <- 0.5

x <- 0:n
prob <- dbinom(x, size = n, prob = p)
df <- data.frame(x = x, prob = prob)

labels = c("head", "tail")
# Plot using ggplot2
ggplot(df, aes(x = factor(labels), y = prob)) +
  geom_col(fill = "black") +
  ylim(0, 1) +
  labs(title = paste("Bernoulli Proability Mass Function (p =", p, ")"),
       x = "Number of Successes",
       y = "P(X = x)") +
  theme_minimal()

```