---
title: "Uniform Distribution"
author: "Sebastián Sánchez Sandí"
date: "2025-07-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let $X$ be a random variable. If X \~ Unif(n), then it follows a discrete uniform distribution over n equally likely outcomes. The probability mass function is given by:

$$
f(x) = \begin{cases} \frac{1}{n} &
\text{if }  a \leq x \leq b \\ 0 &
\text{if } x \leq a \lor x \geq b \end{cases}
$$

Where $n = a + b - 1$, and $x \in \{a, a+1, \dots,b\}$

-   $E(X)=\frac{n+1}{2}$

-   $Var(X)=\frac{n^2-1}{12}$

This distribution models scenarios where all possible outcomes are finite and equally likely. A common example is rolling a fair six-sided die, where each face (1 through 6) has an equal probability of $\frac{1}{6}$.

```{r echo=FALSE}
library(ggplot2)

x <- 1:6
prob <- rep(1/6, 6)
df <- data.frame(x = x, prob = prob)

ggplot(df, aes(x = factor(x), y = prob)) +
  geom_col(fill = "black") +
  ylim(0, 1) +
  theme_minimal() +
  labs(title = "Discrete Uniform Probability Mass Function",
       x = "X", y = "P(X = x)")
```
